---
title: "Web Scraping with R"
author: "Lorna Wildgaard & Christian Knudsen"
date: "9/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Always remember!
Do not scrape websites unethically! Always respect the copyright of the creator(s) of websites.

# tilgang
Ja, vi ved godt at du hellere vil få at vide hvordan du skraber lige præcis den der tekst fra den der helt specifikke side. 
Men ville det ikke være bedre at få et generelt værktøj der kan bruges til en anden tekst fra en anden side?
Så vi bruger en eksempelside med et righoldigt udvalg af data. Når du kan finde ud af det, kan du nok finde ud af at applikere teknikken på en anden side.

# Pre-requisites
R knowledge equivalent to R for absolutte begyndere. 
Svarende til at man ved hvad en variabel er, hvad en datatype er, hvad en dataframe er. Hvad en pipe er.

R og tidyverse, (is rvest actually included?) installed (or use rstudio.cloud - how does that actually work with external websites)
Some knowledge of HTML and CSS. or are we going to cover that here?
Selector Gadget - other browsers than chrome?

# Step 1
Install necessary packages. rvest parses HTML and/or XML files. For date and time manipulation: lubridate. tidyverse for a comprehensive set of packages making everything easier. Readtext package extracts text data from various fromats such as PDF, DOCX and Text Files.
```{r eval=F}
install.packages(c("tidyverse", "lubridate", "rvest", "readtext"))
```

This might take some time.

Load the packages:
```{r}
library(tidyverse)
library(lubridate)
library(rvest)
library(readtext)

# Exercise 1: a brief introduction to how to find the information you need in html
```
# Exercise 2: Scrape a single webpage
As a first step, we will download a single web page from The Guardian and extract text together with relevant metadata such as the article date. Let’s define the URL of the article of interest and load the rvest package, which provides very useful functions for web crawling and scraping.

url <- "https://www.theguardian.com/world/2017/jun/26/angela-merkel-and-donald-trump-head-for-clash-at-g20-summit"
require("rvest")
A convenient method to download and parse a webpage is provided by the function read_html which accepts a URL as its main argument. The function downloads the page and interprets the html source code as an HTML or XML object.

html_document <- read_html(url)

HTML and XML objects are a structured representation of HTML/XML source code, which allows to extract single elements (headlines e.g. <h1>, paragraphs <p>, links <a>, …), their attributes (e.g. <a href="http://...">) or text wrapped in between elements (e.g. <p>my text...</p>). Elements can be extracted in XML objects with XPATH-expressions.

XPATH is a query language that parses XML-tree structures and we use it to select the headline element from the HTML page.

The following xpath expression queries for first-order-headline elements h1, anywhere in the tree // which fulfill a certain condition [...], namely that the class attribute of the h1 element must contain the value content__headline.

The next expression uses R pipe operator %>%, which takes the input from the left side of the expression and passes it on to the function ion the right side as its first argument. The result of this function is either passed onto the next function, via a pipe (%>%) or it is assigned to variable, if it is the last operation in a pipe. Our pipe takes the html_document object, passes it to the html_node function, which extracts the first node fitting the given xpath expression. The resulting node object is passed to the html_text function which extracts the text wrapped in the h1-element.

[NB - det antages herunder at _xpath variablene er fundet ovenfor. De defineres derfor ikke explicit]
  
title_xpath <- "//h1[contains(@class, 'content__headline')]"
title_text <- html_document %>%
  html_node(xpath = title_xpath) %>%
  html_text(trim = T)
Let’s see, what the title_text contains:

cat(title_text)
  
A good rule of thumb in programming is that if you expect to do something more than three times, you should write a function. How do we do that?
  
title_extract <- function(x){
                 print(x)
                 } 

This is a relatively simple function. We define it by assigning the result of another function, function(), to the variable "title_extract", which then becomes a: function.
                 
As we have seen repeatedly with earlier functions, a function is something that takes some sort of input (the input can be nothing), and returns something. In this case the function title_extract() takes some input, for the purposes of what the function does, that is referred to as "x". And this function prints out x. Not that interesting.
                 
Instead we could give the function some more useful features:
title_extract <- function(html){
  result <- html %>%
  html_node(xpath = title_xpath) %>%
  html_text(trim = T)
  return(result)
  }  
  
Now, the function as its input takes html_document. It does the exact same thing we did previously extracting the title, and saved in the variable "result", and finally we ask the function to "return" the result.

That was a bit complicated. But now we can write:

title_text <- title_extract(html_document)
               
It takes a bit longer to write that function. But it saves a lot of typing later.              

## NA
Now we modify the xpath expressions, to extract the article info, the paragraphs of the body text and the article date. Note that there are multiple paragraphs in the article. To extract not only the first, but all paragraphs we utilize the html_nodes function and glue the resulting single text vectors of each paragraph together with the paste0 function.

intro_xpath <- "//div[contains(@class, 'content__standfirst')]//p"
intro_text <- html_document %>%
  html_node(xpath = intro_xpath) %>%
  html_text(trim = T)
cat(intro_text)
## NA
body_xpath <- "//div[contains(@class, 'content__article-body')]//p"
body_text <- html_document %>%
  html_nodes(xpath = body_xpath) %>%
  html_text(trim = T) %>%
  paste0(collapse = "\n")
Now, let’s inspect the first 150 elements of the text body.

cat(substr(body_text, 0, 150))
We now extract the date from the html document.

date_xpath <- "//time"
date_object <- html_document %>%
  html_node(xpath = date_xpath) %>%
  html_attr(name = "datetime") %>%
  as.Date()
cat(format(date_object, "%Y-%m-%d"))
## NA
The variables title_text, intro_text, body_text and date_object now contain the raw data for any subsequent text processing.

We might want to write functions for the individual extracting steps, just like we did earlier with the title text.




# Exercise 3: Following links when the webpages are numbered 
  
[NB Her bliver vi også nødt til at have kigget på html'en og hvordan siden er struktureret i øvelse 1.]
  
This sessions uses the following tutprial: Schweinberger, Martin. 2020. Web Crawling and Scraping using R. Brisbane: The University of Queensland. url:
ttps://slcladal.github.io/webcrawling.html (Version 2020.12.03).

Normally we do not want to download a single document as we might as well copy/paste. In this exercise we'll download a series of documents from the Guardian website, tagged with "Angela Merkel". We want to download the tags and also the exact links to the articles of interest.

url <- "https://www.theguardian.com/world/angela-merkel"
html_document <- read_html(url)

Second, download and scrape each individual article page. 
For this, we extract all href-attributes from a-elements fitting a certain CSS-class. To select the right contents via XPATH-selectors, you need to investigate the HTML
structure of your specific page. Modern browsers such as Firefox and Chrome support you in that task by a function called “Inspect Element” (or similar), available
through a right-click on the page element

links <- html_document %>%
  html_nodes(xpath = "//div[contains(@class, 'fc-item__container')]/a") %>%
  html_attr(name = "href")

Now, links contains a list of 20 hyperlinks to single articles tagged with Angela Merkel

head(links, 3)

But stop! There is not only one page of links to tagged articles. If you have a look on the page in your browser, the tag overview page has several more than 60 sub
pages, accessible via a paging navigator at the bottom. By clicking on the second page, we see a different URL-structure, which now contains a link to a specific paging
number. We can use that format to create links to all sub pages by combining the base URL with the page numbers

page_numbers <- 1:3
base_url <- "https://www.theguardian.com/world/angela-merkel?page="
paging_urls <- paste0(base_url, page_numbers)
# View first 3 urls
head(paging_urls, 3)

Now we can iterate over all URLs of tag overview pages, to collect more/all links to articles tagged with Angela Merkel. We iterate with a for-loop over all URLs and
append results from each single URL to a vector of all links

all_links <- NULL
for (url in paging_urls) {
  # download and parse single ta overview page
  html_document <- read_html(url)
  # extract links to articles
  links <- html_document %>%
    html_nodes(xpath = "//div[contains(@class, 'fc-item__container')]/a") %>%
    html_attr(name = "href")
  
  # append links to vector of all links
  all_links <- c(all_links, links)
}

An effective way of programming is to encapsulate repeatedly used code in a specific function. This function then can be called with specific parameters, process
something and return a result. We use this here, to encapsulate the downloading and parsing of a Guardian article given a specific URL. The code is the same as in our
exercise 1 above, only that we combine the extracted texts and metadata in a data.frame and wrap the entire process in a function-Block.

scrape_guardian_article <- function(url) {
  
  html_document <- read_html(url)
  
  title_xpath <- "//h1[contains(@class, 'content__headline')]"
  title_text <- html_document %>%
    html_node(xpath = title_xpath) %>%
    html_text(trim = T)
  
  intro_xpath <- "//div[contains(@class, 'content__standfirst')]//p"
  intro_text <- html_document %>%
    html_node(xpath = intro_xpath) %>%
    html_text(trim = T)
  
  body_xpath <- "//div[contains(@class, 'content__article-body')]//p"
  body_text <- html_document %>%
    html_nodes(xpath = body_xpath) %>%
    html_text(trim = T) %>%
    paste0(collapse = "\n")
  
  date_xpath <- "//time"
  date_text <- html_document %>%
    html_node(xpath = date_xpath) %>%
    html_attr(name = "datetime") %>%
    as.Date()
  
  article <- data.frame(
    url = url,
    date = date_text,
    title = title_text,
    body = paste0(intro_text, "\n", body_text)
  )
  
  return(article)
  
}

Now we can use that function scrape_guardian_article in any other part of our script. For instance, we can loop over each of our collected links. We use a running
variable i, taking values from 1 to length(all_links) to access the single links in all_links and write some progress output

all_articles <- data.frame()
for (i in 1:length(all_links)) {
  cat("Downloading", i, "of", length(all_links), "URL:", all_links[i], "\n")
  article <- scrape_guardian_article(all_links[i])
  # Append current article data.frame to the data.frame of all articles
  all_articles <- rbind(all_articles, article)
}

Inspect the first three articles and save them:

head(all_articles, 3)
# Write articles to disk
write.csv2(all_articles, file = "data/guardian_merkel.csv")

The last command write the extracted articles to a CSV-file in the data directory for any later use
