---
title: "Web Scraping with R"
author: "Lorna Wildgaard & Christian Knudsen"
date: "9/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Always remember!
Do not scrape websites unethically! Always respect the copyright of the creator(s) of websites.

# tilgang
Ja, vi ved godt at du hellere vil få at vide hvordan du skraber lige præcis den der tekst fra den der helt specifikke side. 
Men ville det ikke være bedre at få et generelt værktøj der kan bruges til en anden tekst fra en anden side?
Så vi bruger en eksempelside med et righoldigt udvalg af data. Når du kan finde ud af det, kan du nok finde ud af at applikere teknikken på en anden side.

# Pre-requisites
R knowledge equivalent to R for absolutte begyndere. 
Svarende til at man ved hvad en variabel er, hvad en datatype er, hvad en dataframe er. Hvad en pipe er.

R og tidyverse, (is rvest actually included?) installed (or use rstudio.cloud - how does that actually work with external websites)
Some knowledge of HTML and CSS. or are we going to cover that here?
Selector Gadget - other browsers than chrome?

# Step 1
Install necessary packages. rvest parses HTML and/or XML files. For date and time manipulation: lubridate. tidyverse for a comprehensive set of packages making everything easier.
```{r eval=F}
install.packages(c("tidyverse", "lubridate", "rvest"))
```

This might take some time.

Load the packages:
```{r}
library(tidyverse)
library(lubridate)
library(rvest)
```

